Points Above Replacement

### 2022-03-01 Code/PointGuardPAR.Rmd
Add files via upload

```{r initialize variables, echo=FALSE}
position<-list(pointGuards$Pos)
games<-list(pointGuards$G)
minutesPlayed<-list(pointGuards$MP)
fieldGoalPercentage<- list(pointGuards$FG.)
threePointPercentage<-list(pointGuards$X3P.)
twoPointPercentage<-list(pointGuards$X2P.)
effectiveFieldGoalPercentage<-list(pointGuards$eFG.)
freeThrowPercentage<-list(pointGuards$FT.)
offensiveRebounds<-list(pointGuards$ORB)
defensiveRebounds<-list(pointGuards$DRB)
totalRebounds<-list(pointGuards$TRB)
assists<-list(pointGuards$AST)
steals<-list(pointGuards$STL)
blocks<-list(pointGuards$BLK)
turnovers<-list(pointGuards$TOV)
personalFouls<-list(pointGuards$PF)
points<-list(pointGuards$PTS)
player<-list(pointGuards$Player)
pointsPerMinute<-list(pointGuards$PPM)
PER<-list(pointGuards$PER)
trueShooting<-list(pointGuards$TS.)
usagePercentage<-list(pointGuards$USG.)
winShares<-list(pointGuards$WS)
winSharesPer48<-list(pointGuards$WS.48)
boxPlusMinus<-list(pointGuards$BPM)
valueOver<-list(pointGuards$VORP)
```

```{r methods, echo=FALSE}
offensivePoints<-function(effectiveFieldGoalPercentage, threePointPercentage, freeThrowPercentage, offensiveRebounds, assists, points, turnovers)
+ {(200*effectiveFieldGoalPercentage)+(300*threePointPercentage)+(100*freeThrowPercentage)+(offensiveRebounds)+(3*assists)+(2*points)-(5*turnovers)}
pgOffensivePoints <- mapply(offensivePoints, effectiveFieldGoalPercentage, threePointPercentage, freeThrowPercentage, offensiveRebounds, assists, points, turnovers)
defensivePoints <- function(defensiveRebounds, totalRebounds, steals, blocks, personalFouls)
+ {(2*defensiveRebounds)+(3*totalRebounds)+(5*steals)+(2*blocks)-(2*personalFouls)}
pgDefensivePoints<-mapply(defensivePoints, defensiveRebounds, totalRebounds, steals, blocks, personalFouls)
positionalAdjustment<-function(minutesPlayed)
+ {((minutesPlayed/48)/72)*(minutesPlayed/2600)}
pgPositionalAdjustment<-mapply(positionalAdjustment, minutesPlayed)
offensiveAndDefensivePoints<-function(pgOffensivePoints, pgDefensivePoints)
+ {pgOffensivePoints+pgDefensivePoints}
pgOffensiveAndDefensivePoints<-mapply(offensiveAndDefensivePoints,pgOffensivePoints,pgDefensivePoints)
pointsPerWin<-function(pgOffensiveAndDefensivePoints, minutesPlayed)
+  {48*((pgOffensiveAndDefensivePoints)/minutesPlayed)*8+16}
pgPointsPerWin<-diag(mapply(pointsPerWin, pgOffensiveAndDefensivePoints, minutesPlayed))
PAR<-function(pgOffensiveAndDefensivePoints, pgPositionalAdjustment, pgPointsPerWin)
+ {(pgOffensiveAndDefensivePoints*pgPositionalAdjustment)/pgPointsPerWin}
pgPAR<-diag(diag(mapply(PAR, pgOffensiveAndDefensivePoints,pgPositionalAdjustment,pgPointsPerWin)))
print('PAR Data')
print(pgPAR)
```

```{r scaling factors, echo=FALSE}
scaledOffensivePoints<-scale(pgOffensivePoints, center = TRUE, scale = TRUE)
scaledDefensivePoints<-scale(pgDefensivePoints, center = TRUE, scale = TRUE)
scaledPositionalAdjustment<-scale(pgPositionalAdjustment, center = TRUE, scale = TRUE)
scaledPointsPerWin<-scale(pgPointsPerWin, center = TRUE, scale = TRUE)
scaledPAR<-scale(pgPAR, center = TRUE, scale = TRUE)
```

@@

@@

print('ANOVA of Multiple Regression with PAR as Y')
anova(multipleRegression)

print('RSE of Multiple Regression with PAR as Y')
sigma(multipleRegression)/mean(pgPAR)
print('RSE of Regression of PPM(X) on PAR(Y)')
sigma(regressionPPMonPAR)/mean(pgPAR)
```

>>>>

```{r initialize variables, echo=FALSE}
position<-list(pointGuards$Pos)
games<-list(pointGuards$G)
minutesPlayed<-list(pointGuards$MP)
fieldGoalPercentage<- list(pointGuards$FG.)
threePointPercentage<-list(pointGuards$X3P.)
twoPointPercentage<-list(pointGuards$X2P.)
effectiveFieldGoalPercentage<-list(pointGuards$eFG.)
freeThrowPercentage<-list(pointGuards$FT.)
offensiveRebounds<-list(pointGuards$ORB)
defensiveRebounds<-list(pointGuards$DRB)
totalRebounds<-list(pointGuards$TRB)
assists<-list(pointGuards$AST)
steals<-list(pointGuards$STL)
blocks<-list(pointGuards$BLK)
turnovers<-list(pointGuards$TOV)
personalFouls<-list(pointGuards$PF)
points<-list(pointGuards$PTS)
player<-list(pointGuards$Player)
pointsPerMinute<-list(pointGuards$PPM)
PER<-list(pointGuards$PER)
trueShooting<-list(pointGuards$TS.)
usagePercentage<-list(pointGuards$USG.)
winShares<-list(pointGuards$WS)
winSharesPer48<-list(pointGuards$WS.48)
boxPlusMinus<-list(pointGuards$BPM)
valueOver<-list(pointGuards$VORP)
teamTotalPoints<-list(pointGuards$TeamTotalPoints)
```

```{r methods, echo=FALSE}
offensivePoints<-function(effectiveFieldGoalPercentage, threePointPercentage, freeThrowPercentage, offensiveRebounds, assists, points, turnovers)
+ {(200*effectiveFieldGoalPercentage)+(300*threePointPercentage)+(100*freeThrowPercentage)+(offensiveRebounds)+(3*assists)+(2*points)-(5*turnovers)}
pgOffensivePoints <- mapply(offensivePoints, effectiveFieldGoalPercentage, threePointPercentage, freeThrowPercentage, offensiveRebounds, assists, points, turnovers)
defensivePoints <-function(defensiveRebounds, totalRebounds, steals, blocks, personalFouls)
+ {(2*defensiveRebounds)+(3*totalRebounds)+(5*steals)+(3*blocks)-(3*personalFouls)}
pgDefensivePoints<-mapply(defensivePoints, defensiveRebounds, totalRebounds, steals, blocks, personalFouls)
offensiveAndDefensivePoints<-function(pgOffensivePoints, pgDefensivePoints)
+ {pgOffensivePoints+pgDefensivePoints}
pgOffensiveAndDefensivePoints<-mapply(offensiveAndDefensivePoints,pgOffensivePoints,pgDefensivePoints)
positionalAdjustment<-function(minutesPlayed, points, teamTotalPoints)
+ {(minutesPlayed/3456)*(points/teamTotalPoints)}
pgPositionalAdjustment<-mapply(positionalAdjustment, minutesPlayed, points, teamTotalPoints)
pointsPerWin<-function(pgOffensiveAndDefensivePoints, minutesPlayed)
+  {48*((pgOffensiveAndDefensivePoints)/minutesPlayed)*8+72}
pgPointsPerWin<-diag(mapply(pointsPerWin, pgOffensiveAndDefensivePoints, minutesPlayed))
PAR<-function(pgOffensiveAndDefensivePoints, pgPositionalAdjustment, pgPointsPerWin)
+ {(pgOffensiveAndDefensivePoints*pgPositionalAdjustment)/pgPointsPerWin}
pgPAR<-diag(diag(mapply(PAR, pgOffensiveAndDefensivePoints,pgPositionalAdjustment,pgPointsPerWin)))
print('PAR Data')
print(pgPAR)
```

```{r scaling factors, echo=FALSE}
scaledOffensivePoints<-scale(pgOffensivePoints, center = TRUE, scale = TRUE)
scaledDefensivePoints<-scale(pgDefensivePoints, center = TRUE, scale = TRUE)
scaledPointsPerWin<-scale(pgPointsPerWin, center = TRUE, scale = TRUE)
scaledPAR<-scale(pgPAR, center = TRUE, scale = TRUE)
```

@@

print('Regression of PAR(X) on VORP(Y)')
PARandVORP<-lm(scaledPAR~pointGuards$VORP)
summary(PARandVORP)
plot(pointGuards$VORP, scaledPAR)

print('Regression of PAR(X) on BPM(Y)')
PARandBPM<-lm(scaledPAR~pointGuards$BPM)
summary(PARandBPM)
plot(pointGuards$BPM, scaledPAR)

@@

print('ANOVA of Multiple Regression with PAR as Y')
anova(multipleRegression)
```
